---
title: "Structural Bioinformatics (pt. 1)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB Statistics 

```{r}
stats <- read.csv("Data Export Summary.csv", row.names=1)
stats
```

```{r}
ans <- round(stats$Total/sum(stats$Total)*100, 2)
names(ans) <- rownames(stats)
ans
```

> Q: What proportion of structures in the PDB are protein?

```{r}
protein <- round(sum(stats$Proteins)/sum(stats$Total)*100, 2)
protein
```

## 2. Using bio3d to analyze protein structure data

Use bio3d package from CRAN. 

```{r}
library(bio3d)

pdb <- read.pdb("1hsg")
pdb
```

```{r}
aa <- get.seq("1ake_A")
aa
```

Download the following through the console (not the Rmd): 
install.packages("bio3d")
install.packages("ggplot2")
install.packages("ggrepel")
install.packages("devtools")
install.packages("BiocManager")

BiocManager::install("msa")
devtools::install_bitbucket("Grantlab/bio3d-view")

```{r}
hits <- NULL
hits$pdb.id <- c('1AKE_A','4X8M_A','6S36_A','6RZE_A','4X8H_A','3HPR_A',
                 '1E4V_A','5EJE_A','1E4Y_A','3X2S_A','6HAP_A','6HAM_A',
                 '4K46_A','4NP6_A','3GMT_A','4PZL_A')

hits
```

# download and parse these structures
# ADK --> BLAST PDB --> ALL ADK STRUCTURES 

Download related PDB files
```{r}
library(bio3d)
files <- get.pdb(hits$pdb.id, path="pdbs", split=TRUE, gzip=TRUE)
```

Align and superpose structures
```{r}
pdbs <- pdbaln(files, fit=TRUE, exefile="msa")
```

```{r}
library(rgl)
library(bio3d.view)
view(pdbs)
```

```{r}
rglwidget(elementId = "tmp")
ids <- basename.pdb(pdbs$id)
```

```{r}
pc <- pca(pdbs)
plot(pc)
```

```{r}
plot(pc, 1:2)
dim(pc$U)
```

make a PCA trajectory 
```{r}
pc1 <- mktrj()
```






