---
title: "Lecture 05: Data Visualization and Graphics in R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Creating a basic line plot
Plot values (1, 2, 3, 4, 5), make the points circles, and color the data blue.
```{r}
plot(1:5, col="blue", typ="o")
```

#Plotting data from a table
Read in data of baby weight vs. age. Use "View(baby)" to view the table.
```{r}
baby <- read.table("bimm143_05_rstats/weight_chart.txt", 
                   header = TRUE)
```

Plot baby weight vs. age. Adjust colors, point type/size/shape, axes labels, and title accordingly. Hint: use "?plot" to read more about the plot function in R.
```{r}
plot(baby$Age, baby$Weight, col="pink", typ="o", 
     xlab= "Age (months)", ylab= "Weight (kg)",
     ylim= c(2,10), main="Baby Weight vs. Age",
     lwd=2, pch=15, cex=1.5)
```

Example plot 
```{r}
plot(1:5, pch=1:5, cex=1:5, col=1:5)
```

#Creating barplots
Read in mouse feature counts data.
```{r}
mouse <- read.table("bimm143_05_rstats/feature_counts.txt", 
                             header = TRUE, sep = "\t")
```

Create a dot plot.
```{r}
dotchart(mouse$Count)
```

Create a barplot. Hint: use "?barplot" and "?par()$mar".
```{r}
par(mar=c(5.1, 12.1, 4.1, 2.1))
barplot(mouse$Count, horiz = TRUE, ylab="", names.arg = mouse$Feature, 
        main="Mouse GRCm38 Genome Features", las=1, xlim=c(0,80000))
```

#Using color in plots
Plot male vs. female counts.
```{r}
mf <- read.delim("bimm143_05_rstats/male_female_counts.txt")
barplot(mf$Count, names.arg = mf$Sample, col=rainbow(10))
```

(This is the output of the rainbow function used to color the barplot above.)
```{r}
rainbow(10)
```

Here is a more effective way to write the code: using nrow rather than a set number (since the number of rows can change).
```{r}
barplot(mf$Count, names.arg=mf$Sample, col=rainbow(nrow(mf)))
```

Color male data one color and female data another color.
```{r}
mf <- read.delim("bimm143_05_rstats/male_female_counts.txt")
barplot(mf$Count, names.arg = mf$Sample, col=c("lightblue", "pink"), las=2)
```



